LSOA domestic Electricty and Gas maps

### 2021-09-03 LSOA domestic Elec and Gas.Rmd
Making the overlay map a bit clearer

# we already checked & transformed the boundaries for leaflet so re-use
leaflet(lsoa_sf_leaflet) %>% 
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addPolygons(color = ~qpal(mean_de_diff),
              fillOpacity = 0.6, weight = 1.5, popup = ~(LSOA11CD ),

>>>>

# we already checked & transformed the boundaries for leaflet so re-use
leaflet(lsoa_sf_leaflet) %>% 
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addPolygons(color = ~qpal(mean_de_diff),
              fillOpacity = 0.6, weight = 1.6, popup = ~(LSOA11CD ),

               highlight = highlightOptions(
                weight = 6,
                color = "#666",
                fillOpacity = 0.8,
                bringToFront = TRUE))
